curacao_threeplayers_rest_monster

### 2020-09-30 inst/curacao1962_threeplayers_rest_monster.Rmd
bugfix
use specificp.gt.test()
slight rearrangement and better description of cncmp

In the above three matrices, each row is a round, and the entries show
the number of matches, collusive matches, and noncollusive matches
played up to and including that round.

@@

We can see the difference between the two players:

@@

@@

  white_player_rested <- a[i,5] - a[i,6] > 1
  black_player_rested <- a[i,6] - a[i,5] > 1

@@

A bit of tidying:

```{r}
aa <- subset(a,a[,5] != a[,6])
aa <- subset(aa,aa[,3] != "1/2-1/2")

>>>>

In the above three matrices, each row is a round, and the entries show
the number of matches, collusive matches, and noncollusive matches
played up to and including that round for each of the 8 players.  Each
(named) column corresponds to a player.  Looking at the last row of
`cumulative_noncollusive_matches` we see that in round 28, players
Petrosian, Keres, and Geller had played a total of 18 noncollusive
matches while the other players had played considerably more and would
be expected to be more fatigued at this point in the tournament.  Note
that Tal retired after round 21 due to illness, which explains why he
had played fewer noncollusive games than Fischer, Korchnoi, Benko, or
Filip at this point.

@@

We can see the differences between cumulative noncollusive games
played between Black and White, summed over the whole tournament:

@@

We can assess a null of no effect of fatigue:

Then Fisher test:
```{r}
aa <- subset(a,a[,5] != a[,6])
aa <- subset(aa,aa[,3] != "1/2-1/2")

Highly signficant.

@@

  white_player_rested <- a[i,6] - a[i,5] > 1
  black_player_rested <- a[i,5] - a[i,6] > 1

@@

 Now a hypothesis test

```{r,label=hyptest,cache=TRUE}
specificp.gt.test(H,"rest",0)
```
